Sky Tomography for 3D Aerosol Distribution Recovery

### 2013-07-26 article.tex
bookmark

The recovery task is phrased as optimization of an objective function,
that fits the image-formation model (\cref{eq:bigIc,eq:bigIA}) to
$N_{\rm views}$ measured photographs $\{ {\bm i}^{\rm
measured}_c\}_{c=1}^{N_{\rm views}}$:
\begin{equation}
  \label{eq:minobjectiveA}
  \hat{\bm n} =
  \argmin_{{\bm n}} F({\bm n})
\end{equation}
where
\begin{equation}
  \label{eq:objectiveA}
  F({\bm n})
  = \sum_{c=1}^{N_{\rm views}}
  \| \Mask \roundy{{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})}\|^2_2 + \eta \cdot \Psi({\bm n})
\end{equation}
Here $\Psi({\bm n})$ is a regularization term that expresses some
prior knowledge on the solution and $\eta$ is the regularization
coefficient.  We enforce smoothness of the solution by using the
\emph{Laplacian} operator.
\begin{equation}
  \label{eq:regularizer}
  \Psi({\bm n}) = \| \nabla^2{\bm n}\|^2_2
\end{equation}
We use $\Mask$ as a weight map to mask the influence of the sun and
the horizon. These regions are prone to dominant multiple scattering.
We solve~\cref{eq:minobjectiveA} using standard optimization tools.
The gradient of $F$ with respect to ${\bm n}$ is
\begin{align}
  \Grad{{\bm n}} F = -2\sum_{c=1}^{N_{\rm views}}
  \transpose{\left[{\bm J}_{{\bm i}_c}({\bm n})\right]} [{\bm i}^{\rm
    measured}_c - {\bm i}_c({\bm n})] + 2 \cdot \eta \cdot
  \nabla^2\nabla^2{\bm n} \;.
  \label{eq:gradient1}
\end{align}
Here the matrix ${\bm J}_{{\bm i}_c}({\bm n})$ is the Jacobian of the
vector ${\bm i}_c$ with respect to ${\bm n}$, and we make use of the
symmetry of the \emph{Laplacian} operator. A close-form expression of
our Jacobian is
\begin{align}
  {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}({\bm A}-{\bm B}){\bm C}
  ,
  \label{eq:gradient2}
\end{align}
where
\begin{align}
  \label{eq:gradient3}
  {\bm A} &= \varpi^{\rm aerosol}\sigma^{\rm aerosol}
  \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)} \nonumber\\
  {\bm B} &= {\sigma}^{\rm aerosol}\transpose{{\bm D}_c} \nonumber\\
  & \;\;\; \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
      aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
      scatter}_c) \odot{\bm n}
    ]} \nonumber \\
  {\bm C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
      aerosol} {\bm D}_c {\bm n})]} \transpose{{\vect{\Pi}}_c}
\end{align}
For a detailed derivation of \cref{eq:gradient2,eq:gradient3}, we
refer the reader to \cref{sec:gradient-derivation}.

>>>>

The recovery task is phrased as optimization of an objective function,
that fits the image-formation model (\cref{eq:bigIc,eq:bigIA}) to
$N_{\rm views}$ measured photographs $\{ {\bm i}^{\rm
measured}_c\}_{c=1}^{N_{\rm views}}$:
\begin{equation}
  \label{eq:minobjectiveA}
  \hat{\bm n} =
  \argmin_{{\bm n}} F({\bm n})
\end{equation}
where
\begin{equation}
  \label{eq:objectiveA}
  F({\bm n})
  = \sum_{c=1}^{N_{\rm views}}
  \| \Mask \roundy{{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})}\|^2_2 + \eta \cdot \Psi({\bm n})
\end{equation}
Here $\Psi({\bm n})$ is a regularization term that expresses some
prior knowledge on the solution and $\eta$ is the regularization
coefficient. 
We use $\Mask$ as a weight map to mask the influence of the sun and
the horizon. These regions are prone to dominant multiple scattering.
One common measurement of smoothness are the second order derivatives.
These can be calculated using the \emph{Laplacian} operator, $\nabla^2$.
We enforce smoothness of the solution by minimizing the signal energy
of the \emph{Laplacian} of the signal
\begin{equation}
  \label{eq:regularizer}
  \Psi({\bm n}) = \| \nabla^2{\bm n}\|^2_2 = \| \Laplacian{\bm n}\|^2_2
\end{equation}
where $\Laplacian$ is a matrix representation of the \emph{Laplacian} operator.

We solve~\cref{eq:minobjectiveA} using standard optimization tools.
The gradient of $F$ with respect to ${\bm n}$ is
\begin{align}
  \Grad{{\bm n}} F = -2\sum_{c=1}^{N_{\rm views}}
  \transpose{\left[{\bm J}_{{\bm i}_c}({\bm n})\right]} [{\bm i}^{\rm
    measured}_c - {\bm i}_c({\bm n})] + 2 \cdot \eta \cdot
  \Laplacian^T\Laplacian{\bm n} \;.
  \label{eq:gradient1}
\end{align}
Here the matrix ${\bm J}_{{\bm i}_c}({\bm n})$ is the Jacobian of the
vector ${\bm i}_c$ with respect to ${\bm n}$. A close-form expression of
our Jacobian is
\begin{align}
  {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}({\bm A}-{\bm B}){\bm C}
  ,
  \label{eq:gradient2}
\end{align}
where
\begin{align}
  \label{eq:gradient3}
  {\bm A} &= \varpi^{\rm aerosol}\sigma^{\rm aerosol}
  \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)} \nonumber\\
  {\bm B} &= {\sigma}^{\rm aerosol}\transpose{{\bm D}_c} \nonumber\\
  & \;\;\; \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
      aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
      scatter}_c) \odot{\bm n}
    ]} \nonumber \\
  {\bm C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
      aerosol} {\bm D}_c {\bm n})]} \transpose{{\vect{\Pi}}_c}
\end{align}
For a detailed derivation of \cref{eq:gradient2,eq:gradient3}, we
refer the reader to \cref{sec:gradient-derivation}.
